Supplemental Materials, Methods and Results

### 2021-05-07 supp.Rmd
Wriyting some results to go along to summarise all tables and figures

## Assessing changes in sexual signals across different body regions
We took measurements of spectral reflectance for different body regions of each chamaleon. In our primary analysis, we averaged across different body regions because we were interested only in whether visual signals overall were different between Kenya and Hawaii. This was justified given that, across the different body regions, effects were largely in a similar direction, and often of similar magnitude (Figures \@ref(fig:FigS2), \@ref(fig:FigS3), \@ref(fig:FigS4) and Tables \@ref(tab:tableS1), \@ref(tab:tableS2), \@ref(tab:tableS3), \@ref(tab:tableS4). \@ref(tab:tableS5)).

@@

@@

@@

>>>>

## Assessing changes in sexual signals across different body regions
We took measurements of spectral reflectance for different body regions of each chamaleon. In our primary analysis, we averaged across different body regions because we were interested only in whether visual signals overall were different between Kenya and Hawaii. This was justified given that, across the different body regions, effects were largely in a similar direction, and often of similar magnitude (Figures \@ref(fig:FigS2) - \@ref(fig:FigS4) and Tables \@ref(tab:tableS1)- \@ref(tab:tableS5)).

@@

Overall, different body regions explained significant variation in achromatic and chromatic contrast in both social contexts, whereas differences between Kenya and Hawaii only existed in achormatic contrast (Figure \@ref(fig:FigS2) & Table \@ref(tab:tableS1)). A significant interaction between body region and population was found for achormatic contrast when males were displaying to each other (Table \@ref(tab:tableS1)). However, in all cases Kenya showed a string reduction in in acromatic contrast relative to Hawaii lizards, despite some variation in the magnitude of effect (Figure \@ref(fig:FigS2)B & D; Table \@ref(tab:tableS2)).

@@

#### Body regions are perceived differently by predators but exhibited similar effect sizes

Chromatic contrast of colour signals against the background varied by predator type, population and body region (Figure \@ref(fig:FigS3)B; Table \@ref(tab:tableS3)). Whereas all body regions in Kenyan chameleons showed a reduced contrast against the background for birds there were small diferences among populations in how snakes perceived colour signals (Figure \@ref(fig:FigS3)A). There were no significant interactions between predator type ('bird' vs 'snake') and either body region or population in achromatic contrast against the background, but a significant population and body region effect (Figure \@ref(fig:FigS3)B; Table \@ref(tab:tableS3)). Effects did not vary by predator type (Table \@ref(tab:tableS3)). Nonetheless, effect sizes across body regions were in the same direction (Figure \@ref(fig:FigS3)B & Table \@ref(tab:tableS4)). Overall, there were significant differences between Kenya and Hawaii in achormatic contrast of the gular and tailbase regions, but not for mid- and top-flank (Table \@ref(tab:tableS5)). In contrast, no sigificant differences between Kenya and Hawaii existed across any body region, whereas significant differences existed between gular, midflank and tailbase (Table \@ref(tab:tableS6)).

@@

#### All body regions exibit similar contrasts between Kenyan and Hawaiian backgrounds suggesting local adaptation of entire visual signal
